% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Ming Zhao}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{zhaoming626@yeah.net}{(+86) 15062376948}{http://mingzhao.me}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Univeristy of Science and Technology of China (USTC)}, Hefei, China}{2014 -- Present}
\textit{Master student} in Software Engineering, expected to graduate July 2017
\datedsubsection{\textbf{Beijing University of Posts and Telecommunication (BUPT)}, Beijing, China}{2010 -- 2014}
\textit{B.S.} in Telecommunication Engineering

\section{\faUsers\ Project Experience}
\datedsubsection{\textbf{USTC. Suzhou Institute for Advanced Study} Jiangsu, China}{2015, 2 -- 2015, 5}
\role{Developer}{Manager: The Open Source Envirocar Community}
Brief introduction: The envirocar community is focused on by collecting vehicle engine related data through OBD2 outlet to build an environment friendly travel style.
\begin{itemize}
  \item The existing pages are written in Php, rewrite it using Javascript. Using leaflet.js, angular.js, openstreet map data to build the front end, the back end analysis system is written using R. The opencpu project connects the frontend and the backend together.
  \item Implement quality check features for the database(Mongoo DB) using PHP.
  \item Investigate methods using semantic web technology to combine the existing data with external data source. 
\end{itemize}

\datedsubsection{\textbf{GreenGPS Project}}{2014, 9 -- 2015, 7}
Brief introduction: A vehicle engine parameters collecting system.
\begin{itemize}
  \item Using Bluetooth to transfer collected data to smart phone, where a UI is designed for users to easy understand current status of the vehicle.
  \item When smart phone is charged, using TCP to transfer data to the server where parameters is inserted into MYSQL database using string parsing techniques, the data collecting related server side is written in JAVA. 
  \item Using Django to build a administrative system, user track can be viewed and managed. Quality check of new track data is run every ten minutes.
\end{itemize}

\section{\faUsers\ Internship}
\datedsubsection{\textbf{Hangzhou Quantum Finance Inc.} Zhejiang, China}{2015, 7 -- 2015, 12}
\role{Summer Intern}{Manager: Xiaofei, Zhao}
Brief introduction: Builing mobile client and related backend to sell finanical products, which is designed using big data and machine learning algorithms.
\begin{itemize}
  \item Responsible for distributing IOS version of the application, incluing distributing under development application for internal and external test.
  \item Responsible for distributing Android version of the application.
  \item Code Review colleage's code.
  \item Responsible for introducing CPCN clearing system(a third payment company), also communicate with staffs with CPCN for payment related problems.
  \item Using JQuery, Ionic, Angular, Cordova to build the mobile application, using Laravel to build the backend server system.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: (JavaScript = Shell) > (Python = PHP = R) > (Java = C++ = C = Matlab = Mathmatica)
  \item Platform: Linux, UCOS, UCGUI, Labview
  \item Development: Web Development, Hardware Development
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Prize}, Award for Academic Performance }{October. 2014}
\datedline{\textit{\nth{2} Prize}, Award for Academic Performance}{October. 2013}
\datedline{\textit{\nth{3} Prize}, National Virtual Instrument Contest}{December. 2013}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/zhaoming626
  \item Languages: English - CET6 560, CET4 611, CEFR B2, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
